The Impact of Immutability on Class Size

### 2020-04-06 paper/article.tex
rename

The Figure~\ref{fig:1} demonstrates the results obtained. The x-axis is
the value of NCSS. The y-axis is the share of immutable classes among
all classes with the given NCSS. The diameter of the plot on the graph
is related to the amount of classes found for the specific NCSS.

@@

@@

>>>>

The Figure~\ref{fig:1} demonstrates the results obtained. The x-axis is
the value of NCSS. The y-axis is the share of immutable classes among
all classes with the given NCSS. The diameter of the plot on the graph
is related to the amount of classes found for the specific NCSS. Classes
with NCSS larger than 1000 are excluded from the graph for the sake of
visual elegancy.

@@

The Figure~\ref{fig:2} demonstrates classes with NCSS lower than 200.

@@

The source code of Ruby and Python scripts used to do the research
is available in GitHub repository \texttt{yegor256/size-vs-immutability}.
